Measurement and Probability in Fuzzy Quantum Theories

### 2017-05-21 prop_iop.tex
prop_iop.tex \subsection{Quantum $\delta$-deterministic Probability Measures} Added...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}

@@

The answer is ``no'' due to the Kochen-Specker theorem whose proof
can also be formulated in the language of cryptodeterministic measure
as in \ref{sec:MerminSquare}.

@@

\subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability
Measures}

@@

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }

@@

The answer is ``no'' due to the Kochen-Specker theorem whose proof
can also be formulated in the language of cryptodeterministic measure
as in section~\ref{subsec:Quantum-I_D-valued-Probability}.

@@

\subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability
Measures\label{subsec:Quantum-I_D-valued-Probability}}

@@

\subsection{Quantum $\delta$-deterministic Probability Measures}

Since there is no quantum $\mathscr{I}_{\mathrm{D}}$-valued probability
measures, we want to know whether there is something which is almost
quantum $\mathscr{I}_{\mathrm{D}}$-valued probability measures. This
gives the following definition.

\begin{definition}An interval-valued probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
is called $\delta$-deterministic if either $\left[l,r\right]\subseteq\left[0,\delta\right]$
or $\left[l,r\right]\subseteq\left[1-\delta,1\right]$ for every $\left[l,r\right]\in\mathscr{I}$.\end{definition}

Given the preceding definition, theorem~\ref{thm:Kochen-Specker-expectation}
says there is no quantum $0$-deterministic probability measures.
In contrast, given a three-dimensional Hilbert space, there is $\frac{1}{3}$-deterministic
probability measures\nb$\iota_{\frac{1}{3}}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} $.
The real problem is if we decrease $\delta$ from $\frac{1}{3}$,
when quantum $\delta$-deterministic probability measures starts to
disappear?
